---
title: "PHM Data Challange 2017"
root.dir: C:/Users/Marcin-Dell/Documents/PHM_Data_challange_2017/
output:
  html_document: default
  html_notebook: default
---
# Loading Data

Loding data and functionas plus some trivial histogram script

```{r Loading Data}
print(getwd())
setwd("../")
source("./R Scripts/Load_data.R")

source("./R/Data_challenge_functions.R")


# exp_tst1 %>%
#     gather() %>%
#     ggplot(aes(value)) +
#     facet_wrap(~ key, scales = "free") +
#     geom_histogram()

```
# Time lag in data
I want to check if there is some lag in the time series data... Due to velocity and progresion of train car on uneaven rails... Let's plot some examples...

```{r}

# exp_tr1 <- load_expetiment(101, dir = "../input/training/", names = TRUE)


# az
plot_groups(train_data %>% filter(ExperimentID == 1 ),
             var = "az",
             par_range = c(1:4),
             lr = "l" ,
             freq_band = 2)

plot_groups(train_data %>% filter(ExperimentID == 1 ),
             var = "az",
             par_range = c(1:4),
             lr = "r" ,
             freq_band = 2)
# azs
plot_groups(train_data %>% filter(ExperimentID == 1 ),
             var = "azs",
             par_range = c(1:2),
             lr = "" ,
             freq_band = 2)

# azp
plot_groups(train_data %>% filter(ExperimentID == 1 ),
             var = "azp",
             par_range = c(1:4),
             lr = "r" ,
             freq_band = 3)

```
There is no time lag in data between sensors!
Someone have already tidied the data for us!
Checked on all types of data and now on different data file:

```{r}


 some_trainig <- train_data %>% filter(ExperimentID == 193 )
lr = "r"
band = 2
# az
plot_groups(some_trainig,
             var = "az",
             par_range = c(1:4),
             lr = lr,
             freq_band = band)
# az
plot_groups(some_trainig,
             var = "az",
             par_range = c(1:4),
             lr ="l",
             freq_band = band)
# azs
# azs
plot_groups(some_trainig,
             var = "azs",
             par_range = c(1:2),
             lr = "" ,
             freq_band = band)

# azp
plot_groups(some_trainig,
             var = "azp",
             par_range = c(1:4),
             lr = lr ,
             freq_band = band)
```

# Paralel Parts

```{r}
band = 1

# az
plot_groups(some_trainig,
             var = "az",
             par_range = 1,
             lr = c("l","r"),
             freq_band = band)

# azp
plot_groups(some_trainig,
             var = "azp",
             par_range = 1,
             lr = c("l","r") ,
             freq_band = band)

# azs
plot_groups(some_trainig,
             var = "azs",
             par_range = c(1:2),
             lr = "" ,
             freq_band = band)
```



# Residules
We will operate on residules to find potential failures or failuer modes.
We know we need to run "detection" of failure type analysis not predictive or cumulative damage models.

```{r Residual calculation example}
# Residual calculation
band = 1

# az
rest_1 <- calc_residules(some_trainig,
             var = "az",
             par_range = 1,
             lr = c("l","r"),
             freq_band = band)

# azp
rest_2 <- calc_residules(some_trainig,
             var = "azp",
             par_range = 1,
             lr = c("l","r") ,
             freq_band = band)

# azs
rest_3 <- calc_residules(some_trainig,
             var = "azs",
             par_range = c(1:2),
             lr = "" ,
             freq_band = band)

```

```{r Apmlitude dumpening rations examples}

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
